Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-23 cloneoverflow-latex/cloneoverflow.tex
Updated the experimental framework diagram. Move things around and fixed small problems (e.g. removed MIT license of Stack Overflow since it is not implemented yet).

\subsection{Clone Detection}

There are a number of restrictions in terms of choosing clone
detection tools for this study. The main restriction is due to nature
of code snippets posted on Stack Overflow, as most of them are
incomplete Java classes or methods. Hence, a detector must be flexible
enough to process code snippets that are not compilable or not
complete blocks. Moreover, since the amount of code that has to be
processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to
report clones in a reasonable amount of time. We have tried 5
state-of-the-art clone detectors including Simian~\cite{simian},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002},
iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against the
Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD
failed with execution errors after running for couple of hours. Thus,
we removed them from the study. Simian and NiCad are flexible enough
to handle code with incomplete methods or classes and successfully
completed the detection.

@@

%We processed two datasets, 144,064 Java code snippets from accepted answers on Stack
%Overflow and 111 open source projects from the Qualitas corpus. 
%The Java code snippets were extracted from Stack Overflow posts. 
We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the accuracy of clone detection. Then, we
deployed the two clone detectors to locate clones between the two
datasets. Due to a scalability issue, we partitioned the input and ran the tools multiple
times. Each run was composed of the entire Stack Overflow data and a
single Qualitas project. We repeated the process until we covered all
111 projects.  We then converted the clone reports to the General
Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a
single GCF file.  Simian did not provide an option to detect
cross-project clones between two locations. Hence the Simian GCF clone
report was filtered to contain only clone pairs between Stack Overflow
and Qualitas projects, removing all clone pairs within either Stack
Overflow or within Qualitas. 
% NiCad provides an option to detect clones
% from two locations so no filtering was needed.

\subsection{Clone Detection Configuration}

@@

\subsection{Filtering Clone Candidates}

@@

\subsubsection{Agreed clone pairs}

As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
agreement filtering using Bellon's criteria\footnote{Similar to the
  original study, we selected a threshold \textit{t} of 0.7 for both
  \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
of \textit{good} clone pairs is 2,313 and the number of \textit{ok}
clone pairs is 32,316, 0.1\textperthousand~of all reported clone
pairs.  Agreed clone pairs are clone pairs that pass Bellon's
\textit{good} or \textit{ok} criteria, and therefore are selected for
manual classification.  Due to NiCad's failures, we do not have NiCad
clones from five Qualitas projects in the agreed clone pairs. Simian
clones of the same projects also disappeared from the agreed clone
pairs since they could not be matched.

@@

\subsubsection{Disagreed clone pairs}

@@

The disagreed clone pairs are clone pairs that are reported by a
single tool, either Simian or NiCad, and do not have agreement with
the other tool. The disagreement can be from a misalignment of clone
lines or completely non-overlapping clones. The disagreed pairs from
Simian include clone pairs in the projects with NiCad's errors (1
project from $N_D$ and 5 from $N_E$).  With the four configuration
combinations, we decided to investigate only $S_D$, and $N_D$, and
dropped $S_E$ and $N_E$ due to their enormous amount of clone pairs
(60 and 250 millions respectively). Moreover, $S_E$ and $N_E$ contain
a large number of false positives due to the recall preference of
their EvaClone configurations.

@@

\subsubsection{Manual Inspection Data Set}

For the manual inspection of clone pairs, we selected all
\textit{good} pairs (2,313) and the \textit{ok} pairs for
$S_D$--$N_D$, $S_E$--$N_D$, and $S_D$--$N_E$ (12,336), but we ignored
20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to
their large number of clones and the very small average clone sizes of
5.95 and 6.28 lines (see \Cref{tab:orig_stats}), leading to a high
probability of being trivial clones. We refer to the set of clone
pairs as the \textit{good} set and the \textit{ok'} set.

Together with the 17,801 (referred as $S_D'$ set) and 83 (referred as
$N_D'$ set) clone pairs after filtering clone pairs from $S_D$ and
$N_D$, we ended up with a set of 32,533 online clone pair candidates
for manual inspection.

@@

\subsection{The Seven Patterns of Online Code Cloning}

As we are interested in the patterns of online code clones, we studied
the 8 patterns of cloning from Kapser et
al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
evaluate its applicability to our study. Using the $S_D$ clone report,
snippets were ranked according to (1)~clone pair frequency,
(2)~popularity (i.e.~number of associated Qualitas projects),
(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
selected these four criteria so that we could cover the online clones
from various aspects. We selected the top 10 from each ranking and
obtained 34 unique Stack Overflow snippets. The snippets were
associated with 697 clone pairs. Using Kapser's cloning patterns, the
clone pairs were categorised into either Customisation or Templating.
However, Kapser's cloning patterns are too broad for our study and a
more suitable and fine-grained classification scheme is needed. After
the preliminary study, we adopted one of Kapser's cloning patterns,
\emph{boiler-plate code} and \emph{API/library protocol}, and defined
6 new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP,
IN, and AC as presented in \Cref{tab:classification_scheme}. Pattern
QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones
that have evidence of being copied from a Qualitas project to Stack
Overflow. The evidence of copying can be found in comments in the
Qualitas source code or in the Stack Overflow post's contents. Pattern
SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with
evidence, in the opposite direction from Stack Overflow to a Qualitas
project. Pattern EX (\textbf{Ex}ternal Sources) is cloning that has
evidence of copying from a single or multiple external sources to
Stack Overflow and to a Qualitas project.  Pattern UD
(\textbf{U}nknown \textbf{D}irection) is cloning that creates
identical or highly similar clones between Qualitas and Stack Overflow
but where we could not find any attribution of copying.

@@

The classification of all 32,533 online clone pairs followed the steps
depicted in \Cref{fig:classification_process}. First, we look at a
pair of clone fragments to see their similarity. If they are
accidentally similar clones after code normalisation or false positive
clones from the clone detection tools, we classify the pair into
\textbf{AC}. If the two fragments are boiler-plate code, the pair is
classified into \textbf{BP}. If they implement the same interface or
inherited the same class and share similar overriding methods, the
pair is classified into \textbf{IN}. If the pair is not \textbf{BP},
\textbf{IN}, or \textbf{AC}, we start a detailed investigation. We
check the corresponding Stack Overflow post, read through it carefully
and look for any evidence mentioning code copying. If evidence of
copying has been found from a Qualitas project, the pair is classified
in \textbf{QS}. In several occasions, we used extra information such
as questions' contents, name of posters, and tags to gain a better
understanding. On the other hand, if the source code from the Qualitas
project mentions copying from Stack Overflow, the pair is classified
into \textbf{SQ}. If there is evidence of copying from an external
source instead of a Qualitas projects, the pair is classified into
\textbf{EX}. Lastly, if there is no evidence of copying in any
direction but the clone fragments are highly similar, we classify them
into \textbf{UD}.

@@

We rely on a manual study to qualitatively investigate the patterns of
online code cloning. To achieve this, we classified all 32,533
selected clone pairs according to the process shown in
\Cref{fig:classification_process}.  Before performing the manual
classification, we created and used an automatic classifier 
to classify {\small\texttt{equals()}}, 
{\small\texttt{hashCode()}} and getters/setters. As shown in
\Cref{tab:online_clone_classification_results}, the automatic
classifier helped us to classify 28,897 clone pairs into
pattern \textbf{BP}.

There were 3,636 pairs left for the manual check. The first author,
who has been working on clone detection research for two years, took
the role of the main investigator performing a manual classification
of the 3,636 clone pairs. By consulting the cloning patterns, the main
investigator went through each clone pair candidate, looked at the
clones, and chose the most appropriate cloning pattern for the pair.
%
To mitigate the human errors of the manual classification, the second
author took the role of the validating investigator, performing a
validation on 10\% (364 pairs) of the clone pairs judged by the main
investigator. After the validation, the classifications from the two
investigators were compared and 64 conflicts were found. The two
investigators discussed and resolved 61 of them while the 3 conflicts
were resolved by involving the third author. The classification
results are shown in \Cref{tab:classification_good_o} and explained in
the following.

\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112
online clone pairs with evidences of cloning from Qualitas projects to
Stack Overflow. They include 3, 14, 86, and 9 pairs from the
\textit{good}, \textit{ok'}, $S_D'$, and $N_D'$ set respectively. Most of
them have a statement in the Stack Overflow post saying that the code
is ``copied'' or ``modified'' from a specific file or class in a
Qualitas project. The most cloned projects are \textsf{hibernate} and
\textsf{spring} with 20 clone pairs, followed by \textsf{eclipse} (15
pairs), and \textsf{hadoop} (12 pairs). The clones are used as
examples and are very similar to their original Qualitas code with
limited modifications.

@@

\textbf{EX: External Sources.} We found 200 online clone pairs with
evidence of cloning from external sources to Stack Overflow. They
include 4, 44, 146, and 6 clone pairs from the \textit{good},
\textit{ok'}, $S_D'$, and $N_D'$ set respectively.

@@

\textbf{Compatible license:} There are 40 pairs which have compatible
licenses such as \emph{Apache license v.2}; \emph{Eclipse Public
  License v.1 (EPLv1)}; or a pair of no license vs.~\emph{Creative
  Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC
  BY-NC-SA 3.0)}. These clones are safe for being reused. Since source
code and text on Stack Overflow posted before 1st March 2016 are
protected by \emph{CC BY-NC-SA 3.0} (and \emph{MIT} license from 1st
March 2016 onwards), we can treat the Stack Overflow code snippets
without licensing information as having \emph{CC BY-NC-SA 3.0} by
default. The \emph{CC BY-NC-SA 3.0} license is relaxed and it only
requests an attribution when reused.

@@

>>>>

To answer the four research questions, we derived three result sets; 
\textit{Reported Clones}, \textit{Filtered Clones}, and \textit{Pattern Clones};
and a manual investigation of online clones. 
For the Reported Clones set, we deployed code clone detection
to locate similar code,~i.e.~clones, between Stack Overflow and 
Qualitas projects. The second result set, Filtered Clones, is derived from the
Reported Clones set by filtering out trivial clones. The last result set,
Pattern Clones, is used to define the online code cloning patterns
for our manual classification. We show the number of clone pairs in the Reported Clones,
Filtered Clones and Pattern Clone result set in \Cref{tab:result_sets}.

With the Reported Clones and Filtered Clones result sets, 
we can observe how many code snippets on
Stack Overflow are reported as clones to/from Qualitas projects
in two aspects: before and after removing trivial clones. 
We explain the approach we used to create to two result sets below.

\begin{table}
	\centering
	\caption{Clone Result Sets}
	\label{tab:result_sets}
	%\small
	\begin{tabular}{lp{3cm}r}
		\hline 
		Result set & Description & Clone pairs \\
		\hline
		Reported Clones & All reported clones & 315,786,118 \\ 
		%\hline 
		Filtered Clones & Clones after filtering & 32,533 \\ 
		Pattern Clones & Clones for defining online cloning patterns & 697 \\
		\hline 
	\end{tabular} 
\end{table}

\subsubsection{Reported Clones Result Set} 
We use clone detection to discover online code clones. 
%\textbf{Clone Detection and Configuration: } 
There are a number of restrictions in terms of choosing clone
detection tools for this study. The main restriction is due to nature
of code snippets posted on Stack Overflow, as most of them are
incomplete Java classes or methods. Hence, a detector must be flexible
enough to process code snippets that are not compilable or not
complete blocks. Moreover, since the amount of code that has to be
processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to
report clones in a reasonable amount of time. We have tried 5
state-of-the-art clone detectors including Simian~\cite{simian},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002},
iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against the
Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD
failed with execution errors after running for couple of hours. Thus,
we removed them from the study. Simian and NiCad are flexible enough
to handle code with incomplete methods or classes and successfully
completed the detection.

@@

%We processed two datasets, 144,064 Java code snippets from accepted answers on Stack
%Overflow and 111 open source projects from the Qualitas corpus. 
%The Java code snippets were extracted from Stack Overflow posts. 
We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the accuracy of clone detection. Then, we
deployed the two clone detectors to locate clones between the two
datasets. Due to a scalability issue, we partitioned the input and ran the tools multiple
times. Each run was composed of the entire Stack Overflow data and a
single Qualitas project. We repeated the process until we covered all
111 projects.  We then converted the clone reports to the General
Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a
single GCF file.  Simian did not provide an option to detect
cross-project clones between two locations. Hence the Simian GCF clone
report was filtered to contain only clone pairs between Stack Overflow
and Qualitas projects, removing all clone pairs within either Stack
Overflow or within Qualitas. 
% NiCad provides an option to detect clones
% from two locations so no filtering was needed.
%\subsection{Clone Detection Configuration}

@@

\subsubsection{Filtered Clones Result Set}

@@

\textbf{Agreed clone pairs: } As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
agreement filtering using Bellon's criteria\footnote{Similar to the
  original study, we selected a threshold \textit{t} of 0.7 for both
  \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
of \textit{good} clone pairs is 2,313 and the number of \textit{ok}
clone pairs is 32,316, 0.1\textperthousand~of all reported clone
pairs.  Agreed clone pairs are clone pairs that pass Bellon's
\textit{good} or \textit{ok} criteria, and therefore are selected for
manual classification.  Due to NiCad's failures, we do not have NiCad
clones from five Qualitas projects in the agreed clone pairs. Simian
clones of the same projects also disappeared from the agreed clone
pairs since they could not be matched.

@@

@@

\textbf{Disagreed clone pairs: }
The disagreed clone pairs are clone pairs that are reported by a
single tool, either Simian or NiCad, and do not have agreement with
the other tool. The disagreement can be from a misalignment of clone
lines or completely non-overlapping clones. The disagreed pairs from
Simian include clone pairs in the projects with NiCad's errors (1
project from $N_D$ and 5 from $N_E$).  With the four configuration
combinations, we decided to investigate only $S_D$, and $N_D$, and
dropped $S_E$ and $N_E$ due to their enormous amount of clone pairs
(60 and 250 millions respectively). Moreover, $S_E$ and $N_E$ contain
a large number of false positives due to the recall preference of
their EvaClone configurations.

@@

%\subsubsection{Filtered Clones Set}
We selected all \textit{good} pairs (2,313) and the \textit{ok} pairs for
$S_D$--$N_D$, $S_E$--$N_D$, and $S_D$--$N_E$ (12,336), but we ignored
20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to
their large number of clones and the very small average clone sizes of
5.95 and 6.28 lines (see \Cref{tab:orig_stats}), leading to a high
probability of being trivial clones. We refer to the set of clone
pairs as the \textit{good} set and the \textit{ok'} set.
Together with the 17,801 (referred as $S_D'$ set) and 83 (referred as
$N_D'$ set) clone pairs after filtering clone pairs from $S_D$ and
$N_D$, we ended up with a set of 32,533 online clone pair candidates
for manual inspection.

@@

\subsection{RQ2: Patterns of Online Code Cloning}
As we are interested in the patterns of online code clones, we studied
the 8 patterns of cloning from Kapser et
al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
evaluate its applicability to our study by using a small subset of the
reported online clones.

\subsubsection{Pattern Clones Result Set}
Using the $S_D$ clone report,
snippets were ranked according to (1)~clone pair frequency,
(2)~popularity (i.e.~number of associated Qualitas projects),
(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
selected these four criteria so that we could cover the online clones
from various aspects. We selected the top 10 from each ranking and
obtained 34 unique Stack Overflow snippets. The snippets were
associated with 697 clone pairs.

\subsubsection{Defining Online Code Cloning Patterns}
Using Kapser's cloning patterns and the Pattern Clones Result Set, the
clone pairs were categorised into either Customisation or Templating.
However, Kapser's cloning patterns are too broad for our study and a
more suitable and fine-grained classification scheme is needed. After
the preliminary study, we adopted one of Kapser's cloning patterns,
\emph{boiler-plate code} and \emph{API/library protocol}, and defined
6 new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP,
IN, and AC as presented in \Cref{tab:classification_scheme}. Pattern
QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones
that have evidence of being copied from a Qualitas project to Stack
Overflow. The evidence of copying can be found in comments in the
Qualitas source code or in the Stack Overflow post's contents. Pattern
SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with
evidence, in the opposite direction from Stack Overflow to a Qualitas
project. Pattern EX (\textbf{Ex}ternal Sources) is cloning that has
evidence of copying from a single or multiple external sources to
Stack Overflow and to a Qualitas project.  Pattern UD
(\textbf{U}nknown \textbf{D}irection) is cloning that creates
identical or highly similar clones between Qualitas and Stack Overflow
but where we could not find any attribution of copying.

@@

The classification of the filtered online clone pairs followed the steps
depicted in \Cref{fig:classification_process}. First, we look at a
pair of clone fragments to see their similarity. If they are
accidentally similar clones after code normalisation or false positive
clones from the clone detection tools, we classify the pair into
\textbf{AC}. If the two fragments are boiler-plate code, the pair is
classified into \textbf{BP}. If they implement the same interface or
inherited the same class and share similar overriding methods, the
pair is classified into \textbf{IN}. If the pair is not \textbf{BP},
\textbf{IN}, or \textbf{AC}, we start a detailed investigation. We
check the corresponding Stack Overflow post, read through it carefully
and look for any evidence mentioning code copying. If evidence of
copying has been found from a Qualitas project, the pair is classified
in \textbf{QS}. In several occasions, we used extra information such
as questions' contents, name of posters, and tags to gain a better
understanding. On the other hand, if the source code from the Qualitas
project mentions copying from Stack Overflow, the pair is classified
into \textbf{SQ}. If there is evidence of copying from an external
source instead of a Qualitas projects, the pair is classified into
\textbf{EX}.
Lastly, if there is no evidence of copying in any
direction but the clone fragments are highly similar, we classify them
into \textbf{UD}.

The first author, who has been working on clone detection research for 
two years, took the role of the main investigator performing a manual 
classification of the filtered clone pairs. By consulting the cloning 
patterns, the main investigator went through each clone pair candidate, 
looked at the clones, and chose the most appropriate cloning pattern 
for the pair. To mitigate the human errors of the manual classification, 
the second author took the role of the validating investigator, performing a
validation on 10\% of the clone pairs judged by the main
investigator. After the validation, the classifications from the two
investigators were compared and conflicts were discussed and resolved.
If the two investigator cannot find a consensus, the third author is 
involved for the final judgement.

@@

We rely on a manual study to qualitatively investigate the patterns of
online code cloning. To achieve this, we classified all 32,533
selected clone pairs according to the process shown in
\Cref{fig:classification_process}.  Before performing the manual
classification, we created and used an automatic classifier 
to classify {\small\texttt{equals()}}, 
{\small\texttt{hashCode()}} and getters/setters. As shown in
\Cref{tab:online_clone_classification_results}, the automatic
classifier helped us to classify 28,897 clone pairs into
pattern \textbf{BP}.
%
There were 3,636 pairs left for the manual check. 
 The classification
results are shown in \Cref{tab:classification_good_o} and explained in
the following.

\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112
online clone pairs with evidences of cloning from Qualitas projects to
Stack Overflow. They include 3, 14, 86, and 9 pairs from the
\textit{good}, \textit{ok'}, $S_D'$, and $N_D'$ set respectively. Most of
them have a statement in the Stack Overflow post saying that the code
is ``copied'', ``borrow'' or ``modified'' from a specific file or class in a
Qualitas project. For example, according to the motivating example in 
\Cref{fig:before-after}, we found evidence in the Stack Overflow 
Post 22315734 saying that \textit{``Actually, you can learn how to compare 
in Hadoop from WritableComparator. Here is an examle that borrows 
some ideas from it.''}

The most cloned projects are \textsf{hibernate} and
\textsf{spring} with 20 clone pairs, followed by \textsf{eclipse} (15
pairs), and \textsf{hadoop} (12 pairs). The clones are used as
examples and are very similar to their original Qualitas code with
limited modifications.

@@

\textbf{EX: External Sources.} We found 200 online clone pairs with
evidence of cloning from external sources to Stack Overflow. 
They include 4, 44, 146, and 6 clone pairs from the \textit{good},
\textit{ok'}, $S_D'$, and $N_D'$ set respectively. All of them
contain statements showing an external source of the cloned code.
For example, Stack Overflow Post 9549009 contains a code comment saying \textit{``Copied 
	shamelessly from org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator,
	changed only the hash algorithm.''}

@@

\textbf{Compatible license:} There are 40 pairs which have compatible
licenses such as \emph{Apache license v.2}; \emph{Eclipse Public
  License v.1 (EPLv1)}; or a pair of no license vs.~\emph{Creative
  Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC
  BY-NC-SA 3.0)}. These clones are safe for being reused. Since source
code and text on Stack Overflow are
protected by \emph{CC BY-NC-SA 3.0}
, we can treat the Stack Overflow code snippets
without licensing information as having \emph{CC BY-NC-SA 3.0} by
default. The \emph{CC BY-NC-SA 3.0} license is relaxed and it only
requests an attribution when reused.

@@

\section{Overall Discussion}
%What can we learn for the results? For example, if a developer explicitly reports in his/her code that the snippet was copied from stackoverfow, are there some benefits? We could notify - for instance - the developer when some new issues related to the snippet are posted on stackoverflow? Or could we force people posting code on SO to explicitly report licensing information? Or, could we implement an intelligent IDE that when pasting code from external resource checks for licensing violation? These of course are only some (crazy?) ideas that could be developed on the top of the results we have achieved with this study...

%We discovered two issues regarding code snippets on Stack Overflow in this study: (1)  outdated online clones on Stack Overflow and (2) missing or incompatible license in Stack Overflow snippets. 
%that there is a considerable amount of cloned code between Stack Overflow that are cloned from 111 projects in the Qualitas corpus. 64 clone pairs are outdated and 358 snippets have incompatible software licenses to their originals. 
To mitigate the problems of outdated online clones and missing or incompatible license on Stack Overflow code snippets, we propose the following actionable items:

\textbf{Preventive measure:} We encourage Stack Overflow to enforce attribution when source code snippets have been copied ``from'' license software projects and posted on Stack Overflow. Moreover, an IDE plug-in that can automatically detect pasted source code and track their origins with licensing check could also prevent the issue of license-violating Stack Overflow code snippets.

\textbf{Detective measure:} A system to detect outdated source code snippets on Stack Overflow is needed. If a code snippet is copied from an external project with other licenses than CC BY-NC-SA, the poster has to provide the information of the project including the original file name and its online repository (if exists). The system can leverage clone detection tools/techniques to periodically locate and check if the cloned snippet is still up-to-date with its original. With such a system, the poster can be notified when the code has been updated in the original project so that he/she can update their code on Stack Overflow accordingly.
